\bibitem{ref1}Avigyan Sinha, Aneesh R P, Malavika Suresh, Nitha Mohan R, Abinaya D, Ashwin G Singerji ``Brain Tumour Detection Using Deep Learning`` \textit{Seventh International conference on Bio Signals, Images, and Instrumentation (ICBSII)}, 2021

\bibitem{ref2}Pär Salander, A Tommy Bergenheim, Katarina Hamberg, Roger Henriksson , ``Pathways from symptoms to medical care: a descriptive study of symptom development and obstacles to early diagnosis in brain tumour patients`` \textit{Family Practice, Volume 16, Issue 2, April 1999, Pages 143–148}

\bibitem{ref3}McKinney PA, ``Brain tumours: incidence, survival, and aetiology,`` \textit{Journal of Neurology, Neurosurgery \& Psychiatry 2004}

\bibitem{ref4}Muhammad Waqas Nadeem, Mohammed A. Al Ghamdi, Muzammil Hussain, Muhammad Adnan Khan, Khalid Masood Khan, Sultan H. Almotiri and Suhail Ashfaq Butt, ``Brain Tumor Analysis Empowered with Deep Learning: A Review, Taxonomy, and Future Challenges`` \textit{Brain Sci.}2020

\bibitem{ref5}Logeswari, T.; Karnan, M.``An improved implementation of brain tumor detection using segmentation based on hierarchical self organizing map.`` \textit{Int. J. Comput. Theory Eng. 2010, 2, 591.}

\bibitem{ref6}Yang, G.; Raschke, F.; Barrick, T.R.; Howe, F.A.``Manifold Learning in MR spectroscopy using nonlinear dimensionality reduction and unsupervised clustering.`` \textit{Magn. Reson. Med. 2015, 74, 868–878. }

\bibitem{ref7}Mansi Lathera, Dr. Parvinder Singh``Investigating Brain Tumor Segmentation and Detection Techniques `` \textit{International Conference on Computational Intelligence and Data Science (ICCIDS 2019)}

\bibitem{ref8}Nandita Goyal and Dr. Bharti Sharma``Image Processing Techniques for Brain Tumor Identification`` \textit{IOP Conf. Ser.: Mater. Sci. Eng. 1022 012011}

\bibitem{ref9}Isselmou Abd El Kader, Guizhi Xu, Zhang Shuai, Sani Saminu, Imran Javaid, Isah Salim Ahmad and Souha Kamhi``Brain Tumor Detection and Classification on MR Images by a Deep Wavelet Auto-Encoder Model`` \textit{Diagnostics 2021}

\bibitem{ref10}Saurabh Kumar, Iram Abid, Shubhi Garg, Anand Kumar Singh and Vivek Jain``BRAIN TUMOR DETECTION USING IMAGE PROCESSING`` \textit{International Journal of Information Sciences and Application (IJISA). ISSN 0974-2255, Vol.11, No.1, 2019, (Special Issue)}

\bibitem{ref11}Ramin Ranjbarzadeh, Abbas Bagherian Kasgari, Saeid JafarzadehGhoushchi, ShokofehAnari, Maryam Naseri \& Malika Bendechache``Brain tumor segmentation based on deep learning and an attention mechanism using MRI multi‑modalities brain images``